
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#",
  tidy = FALSE,
  fig.width = 8,
  fig.height = 8)
```

[![Linux Build Status](https://travis-ci.org/gaborcsardi/secret.svg?branch=master)](https://travis-ci.org/gaborcsardi/secret)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/gaborcsardi/secret?svg=true)](https://ci.appveyor.com/project/gaborcsardi/secret)
[![](http://www.r-pkg.org/badges/version/secret)](http://www.r-pkg.org/pkg/secret)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/secret)](http://www.r-pkg.org/pkg/secret)
[![Coverage Status](https://img.shields.io/codecov/c/github/gaborcsardi/secret/master.svg)](https://codecov.io/github/gaborcsardi/secret?branch=master)

Allow sharing sensitive information, for example passwords, 'API' keys,
etc., in R packages, using public key cryptography.

## Disclaimer

1. Although the package authors did what they could to make sure that
   the package is secure and cryptographically sound, they are not
   security experts.

2. Memory areas for secrets, user passwords, passpharases, private keys and
   other sensitive information, are not securely cleaned after use!
   Technically, the local R process and other processes on the same
   computer, may have access to them. Never use this package on a public
   computer or any system that you don't trust. (Actually, never typing in
   any password on a public computer is good security practice, in general.)

3. Use this package at your own risk!

## Installation

Install the package using the `install-github.me` service:

```{r, eval = FALSE}
source("https://install-github.me/gaborcsardi/secret")
```
    
Or using `devtools`:

```{r, eval = FALSE}
devtools::install_github("gaborcsardi/secret")
```


## Usage

```{r, child="inst/vignette_child/child.Rmd"}
```

## License

MIT © Gábor Csárdi, Andrie de Vries
